Somatosensory Response Changes During Illusory Finger Stretching

### 2024-05-14 manuscript.qmd
Testing with native python build

processdata <- 1
# the processdata flag has two levels:
# 0 - just produce the manuscript and all analyses and figures from processed EEG data
# 1 - do all analyses from scratch using the raw EEG data

@@

# create python environment and install packages
# if (processdata==1){
  install_miniconda()
  use_miniconda('r-reticulate')
  install_python(version="3.10")
  py_install(c('mne', 'numpy', 'scikit-learn', 'matplotlib', 'pandas', 'openpyxl'))
# }

>>>>

processdata <- 0
# the processdata flag has two levels:
# 0 - just produce the manuscript and all analyses and figures from processed EEG data
# 1 - do all analyses from scratch using the raw EEG data

@@

# create python environment and install packages
# if (processdata==1){
  install_miniconda()
  use_miniconda('r-reticulate')
  # install_python(version="3.10")
  py_install(c('mne', 'numpy', 'scikit-learn', 'matplotlib', 'pandas', 'openpyxl'))
# }
